Delay Comparison of Different Switch Architectures

### 2013-11-15 MSReport/MSThesis.tex
Made some progress on the latex and added the function spread_pattern()

\section{Schedulers}
\begin{itemize}
\item How they work
\item Design Philosophy
\item Expected Properties
\end{itemize}
\section{Switch Schedulers}
We consider two different scheduling algorithms used to route packets across a crossbar based switch.  Iterative Slip -- a practical scheme design by Nick McKeown to solve the issues of head of line delay \cite{McKeown}, and QCSMA -- a probabilistic scheduling policy developed and optimized to be full throughput by Libin Jiang \cite{Libin}.

@@

\begin{table}[ht] \caption{TCP Parameters} 
\centering 
\begin{tabular}{c c c}
 \hline\hline 
 Switch & $T_{\text{ecn}}$ & $p_{\text{ecn}}$ \\
  [0.5ex] \hline 
  Benes&23&.5 \\
 SLIP&10&.5 \\
  QCSMA&12&.5  \\
   ideal  QCSMA&10&.9  \\
   %DCSMA&31&25  \\
  [1ex] \hline 
  \end{tabular}
   \label{ecn_table} 
\end{table}

@@

The performance for the different crossbar applications is comparable as can be seen in figure \ref{spreadagg_delay_spread}.

@@

\subsubsection{`Typical' Flows and spread and aggregate}
Finally to explore switch performance in a datacenter setting that supports both  `typical' datacenter loads and some MapReduce like jobs, we subjected the switch to a superposition of the datacenter load and two spread and aggregate loads on servers 1 and 11 as seen in figure \ref{typ_mult2}.  The performance of the crossbar based switches is again comparable (see figure \ref{typ_mult2_delays}), while the Benes switch exhibits significantly higher delays. The largest delays in the Benes switch taking more than three times as long as the worst crossbar design.

As can be seen in figure \ref{mixed_delay_matrix} the long delays are due to the spread and aggregate flows for all the switches, but for the Benes network they do especially badly.  Note that since it is the spread and aggregate flows (all type 2 flows) that suffer, figure \ref{typ_mult2_delays} shows type 2 as being particularly slow.  This is only true because the spread and aggregate flows are heavily delayed as opposed to the spread and aggregate flows slowing down other type 2 flows.  The other very interesting observation to make is that the incast flows in the Benes switch actually fair pretty well.  It is the many to one transmission that cannot take full advantage of the multipath and therefore incurs the large delays.
\begin{figure}%[h]
%	 \includegraphics[width=90mm]{mult2.png}
	\caption{This graph represents the mix of a `typical' load and two spread and aggregate jobs.}
	\label{typ_mult2}
\end{figure}

@@

@@

Notice that there is no effort to save the events that merge discards.  This is because the stochastic events are generated in a memoryless fashion parametrized by the state (i.e. either occur or do not with the same probability at each time step).  The deterministic events are all a function of the state and can be recalculated from the new state that results after the application of an earlier event.  The ACKs are stored in the event$\_$heap, but could in theory also have their own state variable.  Other deterministic events could also be stored in the event$\_$heap depending on the preference of the coder.

\begin{itemize}
\item To illustrate what the functions called by next$\_$event() look like we have the example of:
\item To add a component to the simulator, need to modify:
\item switch statements 
\end{itemize}
\subsection{Auxiliary structures}
\begin{itemize}
\item variable collections and switch statements
\item Data Collector Class
\item Matlab
\item log
\end{itemize}

>>>>

\section{Switch Schedulers}
We consider two different scheduling algorithms used to route packets across a crossbar based switch.  Iterative Slip -- a practical scheme design by Nick McKeown to solve the issues of head of line delay \cite{McKeown}, and QCSMA -- a probabilistic scheduling policy developed and optimized to be full throughput by Libin Jiang \cite{Libin}.

@@

\begin{table}[ht] \caption{TCP Parameters} 
\centering 
\begin{tabular}{c c c}
 \hline\hline 
 Switch & $T_{\text{ecn}}$ & $p_{\text{ecn}}$ \\
  [0.5ex] \hline 
 SLIP&10&.5 \\
  QCSMA&12&.5  \\
   ideal  QCSMA&10&.9  \\
   %DCSMA&31&25  \\
  [1ex] \hline 
  \end{tabular}
   \label{ecn_table} 
\end{table}

@@

The performance for the different schedulers is comparable as can be seen in figure \ref{spreadagg_delay_spread}.

@@

\subsubsection{`Typical' Flows and spread and aggregate}
Finally to explore switch performance in a datacenter setting that supports both  `typical' datacenter loads and some MapReduce like jobs, we subjected the switch to a superposition of the datacenter load and two spread and aggregate loads on servers 1 and 11 as seen in figure \ref{typ_mult2}.  The performance of the crossbar based switches is again comparable (see figure \ref{typ_mult2_delays}).

As can be seen in figure \ref{mixed_delay_matrix} the long delays are due to the spread and aggregate flows for all the switches.  Note that since it is the spread and aggregate flows (all type 2 flows) that suffer, figure \ref{typ_mult2_delays} shows type 2 as being particularly slow.  This is only true because the spread and aggregate flows are heavily delayed as opposed to the spread and aggregate flows slowing down other type 2 flows
\begin{figure}%[h]
%	 \includegraphics[width=90mm]{mult2.png}
	\caption{This graph represents the mix of a `typical' load and two spread and aggregate jobs.}
	\label{typ_mult2}
\end{figure}

@@

\section{Schedulers}
\begin{itemize}
\item How they work
\item Design Philosophy
\item Expected Properties
\end{itemize}

@@

Notice that there is no effort to save the events that the merge() method discards.  This is because the stochastic events are generated in a memoryless fashion parametrized by the state (i.e. either occur or do not with the same probability at each time step).  The deterministic events are all a function of the state and can be recalculated from the new state that results after the application of an earlier event.  The ACKs are stored in the event$\_$heap, but could in theory also have their own state variable.  Other deterministic events could also be stored in the event$\_$heap depending on the preference of the coder.

So to add a component of a simulator it would be necessary to do the following things:
\begin{itemize}
\item Create additional state variable\\
--- This is to facilitate any bookeeping necessary for events generated by this new component
\item Update the Event class to include updates to the new state.\\
--- This consists of two important parts: a modification of variables in the Event class, and an update to the {\it merge()} method, so two events modifying your new state can successfully be merged into one.
\item The creation of a new function to be placed into the next$\_$event() function.\\
--- This new function would have the form of a next$\_${\it new$\_$component}$\_$event() and would calculate the next event that would occur given the current state.
\item Ideally there would also be a control variable allowing for an easy way to remove the component if it is not needed in a simulation.
\end{itemize}

sofkdos;
\begin{itemize}
\item To illustrate what the functions called by next$\_$event() look like we have the example of:
\item To add a component to the simulator, need to modify:
\item switch statements 
\end{itemize}
\subsection{Auxiliary structures}
\begin{itemize}
\item variable collections and switch statements
\item Data Collector Class
\item Matlab
\item log
\end{itemize}
